Species richness destabilizes trophic communities in freshwater ecosystems

### 2020-03-18 manuscript/bef_stability/manuscript.Rmd
Standardized biomass and richness + introduction done

---
title: Species richness destabilizes trophic communities in freshwater ecosystems
author: Alain Danet, Maud Mouchet, Elisa Thébault and Colin Fontaine
date: \today 
output:
  pdf_document:
    fig_caption: true
bibliography: references.bib
---

@@

Cf blutghen for CVsp as portfolio and statistical averaging of species.
Synchrony as insurance hypothesis facing environmental variations.

- Diversity - stability and diversity - biomass / productivity
  - well studied: both experimentally, empirically and theoretically
  - mecanisms:
    - stability: insurance (asynchrony),
    - diversity: overyielding (complementarity)
  - key papers: [@tilman_biodiversity_2006, @loreau_species_2008,
    @thibaut_understanding_2013, @may_will_1972]
  - BUT: less vertical diversity, trophic communities

- Vertical diversity and stability/biomass
  - well studied: theoretically and (experimentally, less)
  - mecanisms:
    - stability: top-down and bottom-up effect
    - biomass: top-down and bottom-up effects (pyramids of biomass)
  - key papers:[@barbier_pyramids_2019, @shanafelt_david_w._stability_nodate]
  - BUT: local stability, little systems

- Environment can drive stability and biomass:
  - forcing: environmental forcing on communities 
  - can lead to misleading effect: @grace_integrative_2016

- Big scope assessment:
  - inconsistency between theoretical and empirical stability
    - theoretical: no cv_sp nor synchrony
  - No studies on stability-richness in empirical trophic communities
    - no effect of trophic structure

- Goal: Assess relation biomass/stability-diversity in empirical trophic communities
  - introduce effect of trophic structure and environment
  - merge gap between theoretical and empirical studies

- What we have done:
  - big empirical dataset
  - rebuilding empirical network
  - assess relationship between environment, community structure and stability

- Research questions:
  - What are the effects of the community structure on total biomass and stability ? 
    1. What are the effects of species richness on total biomass and stability ?
      - effect of species richness
      - effect of trophic group
    2. What are the effects of the community structure on total biomass and stability ?
      - What is the relative effect of the environment relative to the community
	structure ?
      - What is the effect of the community structure on the different
	parts of the stability + total biomass?
	- Effect of horizontal and vertical diversity

@@

# Compute stability, network metrics, etc with ;he new datasets
com_data <- compute_community_temporal_analysis(.op = op_analysis_bbb)
# Compute sem dataset 
sem_data <- compute_sem_dataset(
  com = com_data[["tps_com"]],
  network = com_data[["tps_net"]],
  hab_press = habitat_pressure,
  sync = com_data[["sync"]],
  nmds = NULL,
  basin = st_basin
  )

stab_div_troph <- com_data$tps_bm_troph %>%
  filter(troph_group != 1) %>%
  mutate(troph_group = as.factor(troph_group),
    log_rich = log10(richness_med),
    log_rich_tot = log10(richness_tot),
    log_bm = log10(biomass_med),
    log_stab = log10(biomass_stab)) %>%
  dplyr::select(station, troph_group, biomass_stab, richness_med, richness_tot, log_rich, log_rich_tot, log_stab, log_bm, biomass_med, richness_tot) %>%
  dplyr::left_join(st_basin, by = "station")
```

@@

```{r get-data, cache = FALSE}
library(nlme)
library(piecewiseSEM)
```

@@

```{r mod-div-total}
library(lme4)
ctrl <- lmeControl(opt='optim')
ctrl_lmer <- lmerControl(optCtrl = list(method = 'optimx'))
stab_div_mod <- lmer(
  data = sem_data,
  control = ctrl_lmer,
  formula = log_stab ~ log_rich_tot + (1 | basin)
)
stopifnot(!isSingular(stab_div_mod, tol = 1e-05))
stab_div_boot <- bootMer(stab_div_mod, mySumm2, nsim = 100)
stab_div_ci <- confint(stab_div_boot)
#stab_div_colin <- car::vif(stab_div_mod) not use if one response
stab_div_sum <- piecewiseSEM::rsquared(stab_div_mod, method = "nagelkerke") %>%
  mutate_at(vars(Conditional, Marginal), ~round(., 2))

pred <- ggpredict(stab_div_mod, terms = c("log_rich_tot"), type = "fe")
stab_div_pred <- pred %>%
  as_tibble() %>%
  rename(
    log_stab = predicted,
    log_rich_tot = x,
    basin = group
  )
stab_div_pred %<>%
  mutate(
    stab = 10^log_stab, # FALSE
    rich = 10^log_rich_tot,
    cl10 =  10^conf.low,
    ch10 =  10^conf.high
  )

#
bm_div_mod <- lmer(data = sem_data,
  formula = log_bm ~ log_rich_tot + (1 | basin)
)
bm_div_boot <- bootMer(bm_div_mod, mySumm2, nsim = 100)
bm_div_ci <- confint(bm_div_boot)
bm_div_sum <- piecewiseSEM::rsquared(bm_div_mod, method = "nagelkerke") %>%
  mutate_at(vars(Conditional, Marginal), ~round(., 2))

pred <- ggpredict(bm_div_mod, terms = c("log_rich_tot"), type = "fe")
#plot(pred, add.data = TRUE)
bm_div_pred <- pred %>%
  as_tibble() %>%
  rename(
    log_bm = predicted,
    log_rich_tot = x,
    basin = group
  )

@@

```{r mod-div-troph, fig.show = "hide"}
stab_troph_mod <- lmer(data = na.omit(stab_div_troph),
  formula = log_stab ~ log_rich_tot + troph_group + log_rich_tot:troph_group + (1 | basin)
  #control = ctrl
)
stab_troph_boot <- bootMer(stab_troph_mod, mySumm2, nsim = 100)
stab_troph_ci <- confint(stab_troph_boot)

@@

pred_troph_mod <- ggpredict(stab_troph_mod, terms = c("log_rich_tot", "troph_group"), type = "fe")
#plot(pred_troph_mod, add.data = TRUE)
stab_troph_pred <- pred_troph_mod %>%
  as_tibble() %>%
  rename(
    log_stab = predicted,
    log_rich_tot = x,
    troph_group = group
  )

@@

bm_troph_mod <- lmer(data = na.omit(stab_div_troph),
  #fixed = log_bm ~ log_rich_tot * troph_group,
  formula = log_bm ~ log_rich_tot + troph_group + log_rich_tot:troph_group + (1 | basin)
  #random = ~ 1 + log_rich_tot * troph_group | basin,
  #control = ctrl 
)
bm_troph_boot <- bootMer(bm_troph_mod, mySumm2, nsim = 100)
bm_troph_ci <- confint(bm_troph_boot)

@@

pred_troph_mod <- ggpredict(bm_troph_mod, terms = c("log_rich_tot", "troph_group"), type = "fe")
#plot(pred_troph_mod, add.data = TRUE)
bm_troph_pred <- pred_troph_mod %>%
  as_tibble() %>%
  rename(
    log_bm = predicted,
    log_rich_tot = x,
    troph_group = group
  )

@@

```{r stab-network}
sem_data %>%
  select(sync, cv_sp, ct, t_lvl) %>%
  gather(network, metrics, ct, t_lvl) %>%
  gather(stab_comp, value, sync, cv_sp) %>%
  ggplot(aes(y = value, x = metrics)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(stab_comp ~ network, scales = "free_x")

stab_ct_mod <- lmer(data = sem_data,
  #fixed = log_bm ~ log_rich_tot * troph_group,
  formula = log_stab ~ ct + (1 | basin)
  #random = ~ 1 + log_rich_tot * troph_group | basin,
  #control = ctrl 
)
stab_ct_boot <- bootMer(stab_ct_mod, mySumm2, nsim = 100)
stab_ct_ci <- confint(stab_ct_boot)

@@

pred_stab_ct_mod <- ggpredict(stab_ct_mod, terms = c("ct"), type = "fe")
#plot(pred_troph_mod, add.data = TRUE)
stab_ct_pred <- pred_stab_ct_mod %>%
  as_tibble() %>%
  rename(
    log_bm = predicted,
    log_rich_tot = x,
    troph_group = group
  )

@@

stab_tlvl_mod <- lmer(data = sem_data,
  #fixed = log_bm ~ log_rich_tot * troph_group,
  formula = log_stab ~ t_lvl + (1 | basin)
  #random = ~ 1 + log_rich_tot * troph_group | basin,
  #control = ctrl 
)
stab_tlvl_boot <- bootMer(stab_tlvl_mod, mySumm2, nsim = 100)
stab_tlvl_ci <- confint(stab_tlvl_boot)

@@

pred_stab_tlvl_mod <- ggpredict(stab_tlvl_mod, terms = c("t_lvl"), type = "fe")
#plot(pred_troph_mod, add.data = TRUE)
stab_tlvl_pred <- pred_stab_tlvl_mod %>%
  as_tibble() %>%
  rename(
    log_bm = predicted,
    log_rich_tot = x,
    troph_group = group
  )

@@

rich_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm", pred = "log_rich_tot")
tlvl_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm", pred = "t_lvl")
RC1_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm", pred = "log_RC1")
```

@@

# effect of env on bm 
env_on_bm <- get_env_on_bm(fit = bm_all_params, p_val_thl = 0.05)
# env on com 
env_on_t_lvl <- get_env_on_com(fit = bm_all_params,
  p_val_thl = 0.05,
  com = "t_lvl")
env_on_ct <- get_env_on_com(fit = bm_all_params,
  p_val_thl = 0.05,
  com = "ct")
env_on_richness <- get_env_on_rich(fit = bm_all_params,
  p_val_thl = 0.05)
```

```{r get-bm-tot-effect-rich}
rich_on_bm <- get_rich_on_bm(fit = bm_all_params,
  p_val_thl = 0.05)
```

@@

sync_on_stab <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_stab", pred = "log_sync")
cv_sp_on_stab <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_stab", pred = "log_cv_sp")
RC1_on_sync <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_sync", pred = "log_RC1")
```

@@

env_on_stab <- get_env_on_stab(fit = all_params, p_val_thl = 0.05)
# effect of env on sync and cv_sp
env_on_sync <- get_env_on_stab_comp(fit = all_params,
  p_val_thl = 0.05,
  stab_comp = "log_sync")
env_on_cv_sp <- get_env_on_stab_comp(fit = all_params,
  p_val_thl = 0.05,
  stab_comp = "log_cv_sp")
# env on com 
env_on_t_lvl <- get_env_on_com(fit = all_params,
  p_val_thl = 0.05,
  com = "t_lvl")
env_on_ct <- get_env_on_com(fit = all_params,
  p_val_thl = 0.05,
  com = "ct")
env_on_richness <- get_env_on_rich(fit = all_params,
  p_val_thl = 0.05)
```

```{r get-sem-tot-effect-rich}
rich_on_stab <- get_rich_on_stab(fit = all_params,
  p_val_thl = 0.05)
rich_on_sync <- get_rich_on_stab_comp(fit = all_params,
  p_val_thl = 0.05,
  stab_comp = "log_sync")
rich_on_cv_sp <- get_rich_on_stab_comp(fit = all_params,
  p_val_thl = 0.05,
  stab_comp = "log_cv_sp")
```

@@

```{r}
richness_lab <- "Total richness (Log 10)"
stab_lab <- "Biomass stability (Log 10)"
bm_lab <- "Total biomass (Log 10)"

@@

```{r p-s-div, fig.cap = stab_div_caption}
lim_log_stab <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_stab")
lim_log_rich_tot <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_rich_tot")
# Plot left

p_stab_div <- sem_data %>%
  ggplot(aes(x = log_rich_tot, y = log_stab))+
  geom_point() +
  ylim(lim_log_stab) +
  xlim(lim_log_rich_tot) +
  labs(x = richness_lab, y = stab_lab) +
  geom_line(data = stab_div_pred) +
  geom_ribbon(data = stab_div_pred, aes(ymin = conf.low, ymax = conf.high), fill
  = "grey20", alpha = .2) +
  annotate("text", x = 1.0, y = .8, label = make_label_rsq(rsq = stab_div_sum),
    parse = TRUE)

# Right plot
p_stab_div_troph <- stab_div_troph %>%
  ggplot(aes(x = log_rich_tot, y = log_stab, color = troph_group)) +
  geom_point() +
  ggplot2::scale_color_manual(
    labels = troph_group_labeller(),
    values = c("blue", "green", "red"),
    name = "Trophic group"
  ) +
  ylim(lim_log_stab) +
  xlim(lim_log_rich_tot) +
  geom_line(data = stab_troph_pred) +
  geom_ribbon(data = stab_troph_pred,
    aes(ymin = conf.low, ymax = conf.high, color = NULL, group = troph_group),
    alpha = .2) +
  annotate("text", x = 0.8, y = .8, label = make_label_rsq(rsq = stab_troph_sum),
    parse = TRUE) +
  #scale_x_log10() + scale_y_log10() +
  labs(x = richness_lab, y = stab_lab)

@@

```{r p-p-div}
lim_log_bm <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_bm")

p_bm_div <- sem_data %>%
  ggplot(aes(x = log_rich_tot, y = log_bm))+
  geom_point() +
  ylim(lim_log_bm) +
  xlim(lim_log_rich_tot) +
  labs(x = richness_lab, y = bm_lab) +
  geom_line(data = bm_div_pred) +
  geom_ribbon(data = bm_div_pred, aes(ymin = conf.low, ymax = conf.high), fill
  = "grey20", alpha = .2) +
  annotate("text", x = .8, y = 1.5, label = make_label_rsq(rsq = bm_div_sum),
    parse = TRUE)

p_bm_div_troph <- stab_div_troph %>%
  ggplot(aes(x = log_rich_tot, y = log_bm, color = troph_group)) +
  geom_point() +
  ylim(lim_log_bm) +
  xlim(lim_log_rich_tot) +
  ggplot2::scale_color_manual(
    labels = troph_group_labeller(),
    values = c("blue", "green", "red"),
    name = "Trophic group"
  ) +
  geom_line(data = bm_troph_pred) +
  geom_ribbon(data = bm_troph_pred,
    aes(ymin = conf.low, ymax = conf.high, color = NULL, group = troph_group),
    alpha = .2) +
  annotate("text", x = 0.8, y = 1.5, label = make_label_rsq(rsq = bm_troph_sum),
    parse = TRUE) +
  #scale_x_log10() + scale_y_log10() +
  labs(x = richness_lab, y = bm_lab)

>>>>

---
title: Species richness destabilizes trophic communities in freshwater ecosystems
author: Alain Danet, Maud Mouchet, Elisa Thébault and Colin Fontaine
date: \today 
output:
  pdf_document:
    fig_caption: yes
fontsize: 12pt
header-includes:
   - \usepackage{setspace}
   - \doublespacing
geometry: margin=2cm
bibliography: references.bib
---

@@

Determining the shape of the relationship between species diversity and ecosystem
functioning has been a central research topic in ecology [@may_will_1972,
@hector_plant_1999, @loreau_biodiversity_2001, @hooper_effects_2005,
@duffy_why_2009, @isbell_forest_quantifying_2018]. Current biodiversity losses
in all ecosystems challenge scientists to understand how ecosystems will be
affected in turn. Studies in Bioversity-Ecosystem Functioning (BEF) usually
quantify species diversity as species richness (i.e number of species) while
ecosystem functioning is quantified as total biomass, productivity (biomass
produced by unit of time) or stability which is quantified in more diverse ways
such as the variability of species abundance, the resilience to perturbation, or
resistance to perturbation [@donohue_navigating_2016].

---
#- Diversity - stability and diversity - biomass / productivity
  #- well studied: both experimentally, empirically and theoretically
  #- mecanisms:
    #- stability: insurance (asynchrony),
    #- diversity: overyielding (complementarity)
  #- key papers: [@tilman_biodiversity_2006, @loreau_species_2008,
    #@thibaut_understanding_2013, @may_will_1972]
  #- BUT: less vertical diversity, trophic communities
---

Species richness has been reported to increase productivity in grasslands
[@grace_integrative_2016], but complex links between between species richness,
environment, productivity and total biomass showed that species richness
decrease total biomass [@grace_integrative_2016] contrary to previous
assessment [@hector_plant_1999, @tilman_biodiversity_2014] because of
competition for light between plants [@grace_integrative_2016]. Complementarity
between species in resource exploitation [@cardinale_species_2002] leading to
overyielding (CHECK) has been proposed to explain positive relationship between
productivity
and species richness, while species richness effect can also rise from the
statistical probability to end up with a highly productive species . The
relationship between species richness and stability is even more complex
partly because of the inherent multidimensionality of stability
[@donohue_dimensionality_2013, @donohue_navigating_2016] and because of the
different metrics of stability privileged in theoretical (stability of local
equilibrium, robustness to primary extinction) and empirical work (variability
of abundance or biomass through time). @may_will_1972 stimulated a lot of
debate and fecund research, showing that species richness, probability of
interacting and average interaction strength destabilizes communities in which
species interact randomly. Empirically, consistent works showed that species
richness increased community stability in grasslands [@tilman_biodiversity_2006],
mesocosms [@pennekamp_biodiversity_2018] and vertebrates
[@olivier_independent_nodate, @franssen_annual_2011]. Two components can
explain variation of community stability, (1) individual species stability and (2)
the species synchrony [@loreau_species_2008, @thibaut_understanding_2013].
Positive [@tilman_biodiversity_2006], neutral [@jiang_different_2009, @olivier_independent_nodate]
and negative [@franssen_annual_2011, @olivier_independent_nodate] relationships
between species stability and species richness have been found.
On the other side, studies consistently found that species richness decreased
synchrony between species [@loreau_species_2008, @thibaut_understanding_2013,
@bluthgen_land_2016; @olivier_independent_nodate]. However, as far as we know,
less studies have reported empirical assessment of stability-richness
relationship in trophic network [but see @thebault_stability_2010].

Conversely, an extensive literature exists on the effects of network structure
on stability in mutualistic and trophic networks [@angelis_stability_1975, @stouffer_,
@thebault_stability_2010, @barbier_pyramids_2019,
@shanafelt_david_w._stability_nodate, add ref]. Particularly, in trophic
networks, most studies are theoretical and consider asymptotic stability to
small perturbation. Studies showed that compartimentalization [@stouffer_] can
increase persistence, while nestedness can either increase [@bascompte,
@thebault_stability_2010] or decrease persistence [@thebault_stability_2010].
Connectance can decrease [@thebault_stability_2010] or increase
[@angelis_stability_1975] resilience of trophic network depending on the
functioning of networks [@angelis_stability_1975].

---
#- Vertical diversity and stability/biomass
  #- well studied: theoretically and (experimentally, less)
  #- mecanisms:
    #- stability: top-down and bottom-up effect
    #- biomass: top-down and bottom-up effects (pyramids of biomass)
  #- key papers:[@barbier_pyramids_2019, @shanafelt_david_w._stability_nodate]
  #- BUT: local stability, little systems 
---

Trophic network are assembled both vertically and horizontally. Studies showed
that the vertical position in the trophic network as well as the strength of
top-down and bottom-up regulation determine biomass and stability at
equilibrium  [@shanafelt_david_w._stability_nodate, @barbier_pyramids_2019].
However studies on stability-diversity have focused on either vertical
diversity or horizontal but rarely both. @zhao_horizontal_2019 have shown that
horizontal and vertical diversity respectively increase and decrease stability
in plankton communities.

---
#- Big scope assessment:
  #- inconsistency between theoretical and empirical stability
    #- theoretical: no cv_sp nor synchrony
  #- No studies on stability-richness in empirical trophic communities
    #- no effect of trophic structure
---

A large inconsistency remains between theoretical and empirical assessment of
stability-diversity in trophic communities. Theoretical studies have
ignored temporal variability and the relative contribution of synchrony and
species variability while empirical studies about temporal variability in natural 
communities have ignored trophic communities and the effect of trophic structure.

---
#- Goal: Assess relation biomass/stability-diversity in empirical trophic communities
  #- introduce effect of trophic structure and environment
  #- merge gap between theoretical and empirical studies
---

---
#- What we have done:
  #- big empirical dataset
  #- rebuilding empirical network
  #- assess relationship between environment, community structure and stability
---

Our goal was to assess stability-diversity in natural trophic community with the
effect of the trophic structure. We combined together the effect of vertical
and horizontal diversity and thus aimed to bridge the gap between theoretical
and empirical studies. We used an standardized monitoring of freshwater fish
communities in french streams. More than three hundreds sites were followed
more than 10 years on the 1995-2018 period. We inferred four thousands potential
interaction networks corresponding to each sampling event, based on size
relationships and knowledge about their ontogenic diet shift.

---
#- Research questions:
  #- What are the effects of the community structure on total biomass and stability ? 
    #1. What are the effects of species richness on total biomass and stability ?
      #- effect of species richness
      #- effect of trophic group
    #2. What are the effects of the community structure on total biomass and stability ?
      #- What is the relative effect of the environment relative to the community
	#structure ?
      #- What is the effect of the community structure on the different
	#parts of the stability + total biomass?
	#- Effect of horizontal and vertical diversity
---

We investigated the effects of the community structure on total biomass and on
synchrony and species variability, which in turn determine community
variability. We have also included the effect of environmental drivers which
can directly affect community variability or indirectly via community structure.
Finally, we assessed the effect of horizontal diversity on trophic group
biomass and variability.

---
#- Environment can drive stability and biomass:
  #- forcing: environmental forcing on communities 
  #- can lead to misleading effect: @grace_integrative_2016
---

@@

# Compute stability, network metrics, etc with ;he new datasets
#debug(summarise_network_over_time)
##myload(network_metrics, dir = mypath("data", "classes"))
#network_metrics %>%
  #left_join(op_analysis, by = "opcod") %>%
  #select(opcod, station, composition) %>%
  #unnest(composition) %>%
  #group_by(station, troph_group) %>%
  #summarise(richness_tot = length(unique(species)))
com_data <- compute_community_temporal_analysis(.op = op_analysis_bbb)
# Compute sem dataset 
sem_data <- compute_sem_dataset(
  com = com_data[["tps_com"]],
  network = com_data[["tps_net"]],
  hab_press = habitat_pressure,
  sync = com_data[["sync_std"]],
  nmds = NULL,
  basin = st_basin
  )

stab_div_troph <- com_data$tps_bm_troph %>%
  filter(troph_group != 1) %>%
  mutate(troph_group = as.factor(troph_group),
    log_rich = log10(richness_med),
    log_rich_std = log10(rich_std_med),
    log_rich_tot = log10(richness_tot),
    log_rich_tot_std = log10(rich_tot_std),
    log_bm = log10(biomass_med),
    log_bm_std = log10(bm_std_med),
    log_stab = log10(biomass_stab),
    log_stab_std = log10(bm_std_stab)
    ) %>%
  dplyr::select(station, troph_group, biomass_stab, richness_med, richness_tot, log_rich, log_rich_std, log_rich_tot, log_rich_tot_std, log_stab, log_stab_std, log_bm, log_bm_std, biomass_med, bm_std_med, richness_tot, rich_tot_std) %>%
  dplyr::left_join(st_basin, by = "station")
```

@@

@@

```{r get-data, cache = FALSE}
library(nlme)
library(piecewiseSEM)
library(lme4)
ctrl <- lmeControl(opt='optim')
ctrl_lmer <- lmerControl(optCtrl = list(method = 'optimx'))
```

```{r mod-div-total}
stab_div_mod <- lmer(
  data = sem_data,
  control = ctrl_lmer,
  formula = log_stab_std ~ log_rich_tot_std + (1 | basin)
)
stopifnot(!isSingular(stab_div_mod, tol = 1e-05))
stab_div_boot <- bootMer(stab_div_mod, mySumm2, nsim = 100)
stab_div_ci <- confint(stab_div_boot)
#stab_div_colin <- car::vif(stab_div_mod) not use if one response
stab_div_sum <- piecewiseSEM::rsquared(stab_div_mod, method = "nagelkerke") %>%
  mutate_at(vars(Conditional, Marginal), ~round(., 2))

pred <- ggpredict(stab_div_mod, terms = c("log_rich_tot_std"), type = "fe")
stab_div_pred <- pred %>%
  as_tibble() %>%
  rename(
    log_stab_std = predicted,
    log_rich_tot_std = x,
    basin = group
  )
stab_div_pred %<>%
  mutate(
    stab = 10^log_stab_std, # FALSE
    rich = 10^log_rich_tot_std,
    cl10 =  10^conf.low,
    ch10 =  10^conf.high
  )

#
bm_div_mod <- lmer(data = sem_data,
  formula = log_bm_std ~ log_rich_tot_std + (1 | basin)
)
bm_div_boot <- bootMer(bm_div_mod, mySumm2, nsim = 100)
bm_div_ci <- confint(bm_div_boot)
bm_div_sum <- piecewiseSEM::rsquared(bm_div_mod, method = "nagelkerke") %>%
  mutate_at(vars(Conditional, Marginal), ~round(., 2))

pred <- ggpredict(bm_div_mod, terms = c("log_rich_tot_std"), type = "fe")
#plot(pred, add.data = TRUE)
bm_div_pred <- pred %>%
  as_tibble() %>%
  rename(
    log_bm_std = predicted,
    log_rich_tot_std = x,
    basin = group
  )

@@

```{r mod-div-troph, fig.show = "hide"}
stab_troph_mod <- lmer(data = stab_div_troph,
  formula = log_stab_std ~ log_rich_tot_std + troph_group + log_rich_tot_std:troph_group + (1 | basin)
  #control = ctrl
)
stab_troph_boot <- bootMer(stab_troph_mod, mySumm2, nsim = 200)
stab_troph_ci <- confint(stab_troph_boot)

@@

pred_troph_mod <- ggpredict(stab_troph_mod, terms = c("log_rich_tot_std", "troph_group"), type = "fe")
#plot(pred_troph_mod, add.data = TRUE)
stab_troph_pred <- pred_troph_mod %>%
  as_tibble() %>%
  rename(
    log_stab_std = predicted,
    log_rich_tot_std = x,
    troph_group = group
  )

@@

bm_troph_mod <- lmer(data = na.omit(stab_div_troph),
  #fixed = log_bm ~ log_rich_tot * troph_group,
  formula = log_bm_std ~ log_rich_tot_std + troph_group + log_rich_tot_std:troph_group + (1 | basin)
  #random = ~ 1 + log_rich_tot * troph_group | basin,
  #control = ctrl 
)
bm_troph_boot <- bootMer(bm_troph_mod, mySumm2, nsim = 100)
bm_troph_ci <- confint(bm_troph_boot)

@@

pred_troph_mod <- ggpredict(bm_troph_mod, terms = c("log_rich_tot_std", "troph_group"), type = "fe")
#plot(pred_troph_mod, add.data = TRUE)
bm_troph_pred <- pred_troph_mod %>%
  as_tibble() %>%
  rename(
    log_bm_std = predicted,
    log_rich_tot_std = x,
    troph_group = group
  )

@@

```{r stab-network, fig.show = "hide"}
sem_data %>%
  select(sync, cv_sp, ct, t_lvl) %>%
  gather(network, metrics, ct, t_lvl) %>%
  gather(stab_comp, value, sync, cv_sp) %>%
  ggplot(aes(y = value, x = metrics)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(stab_comp ~ network, scales = "free_x")

stab_ct_mod <- lmer(data = sem_data,
  #fixed = log_bm ~ log_rich_tot * troph_group,
  formula = log_stab_std ~ ct + (1 | basin)
  #random = ~ 1 + log_rich_tot * troph_group | basin,
  #control = ctrl 
)
stab_ct_boot <- bootMer(stab_ct_mod, mySumm2, nsim = 100)
stab_ct_ci <- confint(stab_ct_boot)

@@

pred_stab_ct_mod <- ggpredict(stab_ct_mod, terms = c("ct"), type = "fe")
#plot(pred_troph_mod, add.data = TRUE)
stab_ct_pred <- pred_stab_ct_mod %>%
  as_tibble() %>%
  rename(
    log_stab_std = predicted,
    log_rich_tot_std = x,
    troph_group = group
  )

@@

stab_tlvl_mod <- lmer(data = sem_data,
  #fixed = log_bm ~ log_rich_tot * troph_group,
  formula = log_stab_std ~ t_lvl + (1 | basin)
  #random = ~ 1 + log_rich_tot * troph_group | basin,
  #control = ctrl 
)
stab_tlvl_boot <- bootMer(stab_tlvl_mod, mySumm2, nsim = 100)
stab_tlvl_ci <- confint(stab_tlvl_boot)

@@

pred_stab_tlvl_mod <- ggpredict(stab_tlvl_mod, terms = c("t_lvl"), type = "fe")
#plot(pred_troph_mod, add.data = TRUE)
stab_tlvl_pred <- pred_stab_tlvl_mod %>%
  as_tibble() %>%
  rename(
    log_stab_std = predicted,
    log_rich_tot_std = x,
    troph_group = group
  )

@@

rich_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "log_rich_tot_std")
tlvl_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "t_lvl")
RC1_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "log_RC1")
```

@@

# effect of env on bm 
env_on_bm <- get_env_on_bm(fit = bm_all_params, p_val_thl = 0.05,
  type = "std")
# env on com 
env_on_t_lvl <- get_env_on_com(fit = bm_all_params, p_val_thl = 0.05,
  com = "t_lvl", type = "std")
env_on_ct <- get_env_on_com(fit = bm_all_params,
  p_val_thl = 0.05, com = "ct", type = "std")
env_on_richness <- get_env_on_rich(fit = bm_all_params,
  p_val_thl = 0.05, type = "std")
```

```{r get-bm-tot-effect-rich}
tot_rich_on_bm <- get_rich_on_bm(fit = bm_all_params,
  p_val_thl = 0.05, type = "std")
```

@@

sync_on_stab <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_stab_std", pred = "log_sync")
cv_sp_on_stab <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_stab_std", pred = "log_cv_sp")
RC1_on_sync <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_sync", pred = "log_RC1")
```

@@

env_on_stab <- get_env_on_stab(fit = all_params, p_val_thl = 0.05,
  type = "std")
# effect of env on sync and cv_sp
env_on_sync <- get_env_on_stab_comp(fit = all_params,
  p_val_thl = 0.05,
  stab_comp = "log_sync", type = "std")
env_on_cv_sp <- get_env_on_stab_comp(fit = all_params,
  p_val_thl = 0.05,
  stab_comp = "log_cv_sp", type = "std")
# env on com 
env_on_t_lvl <- get_env_on_com(fit = all_params,
  p_val_thl = 0.05,
  com = "t_lvl", type = "std")
env_on_ct <- get_env_on_com(fit = all_params,
  p_val_thl = 0.05,
  com = "ct", type = "std")
env_on_richness <- get_env_on_rich(fit = all_params,
  p_val_thl = 0.05, type = "std")
```

```{r get-sem-tot-effect-rich}
rich_on_stab <- get_rich_on_stab(fit = all_params,
  p_val_thl = 0.05, type = "std")
rich_on_sync <- get_rich_on_stab_comp(fit = all_params,
  p_val_thl = 0.05,
  stab_comp = "log_sync", type = "std")
rich_on_cv_sp <- get_rich_on_stab_comp(fit = all_params,
  p_val_thl = 0.05,
  stab_comp = "log_cv_sp", type = "std")
```

@@

```{r}
richness_lab <- "Total richness (m2^-1) (Log 10)"
stab_lab <- "Biomass stability (Log 10)"
bm_lab <- "Total biomass (g/m2) (Log 10)"

@@

```{r p-s-div, fig.cap = stab_div_caption}
lim_log_stab <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_stab_std")
lim_log_rich_tot <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_rich_tot_std")
# Plot left

p_stab_div <- sem_data %>%
  ggplot(aes(x = log_rich_tot_std, y = log_stab_std))+
  geom_point() +
  ylim(lim_log_stab) +
  xlim(lim_log_rich_tot) +
  labs(x = richness_lab, y = stab_lab) +
  geom_line(data = stab_div_pred) +
  geom_ribbon(data = stab_div_pred, aes(ymin = conf.low, ymax = conf.high), fill
  = "grey20", alpha = .2) +
  annotate("text", x = 1.0, y = .8, label = make_label_rsq(rsq = stab_div_sum),
    parse = TRUE)

# Right plot
p_stab_div_troph <- stab_div_troph %>%
  ggplot(aes(x = log_rich_tot_std, y = log_stab_std, color = troph_group)) +
  geom_point() +
  ggplot2::scale_color_manual(
    labels = troph_group_labeller(),
    values = c("blue", "green", "red"),
    name = "Trophic group"
  ) +
  ylim(lim_log_stab) +
  xlim(lim_log_rich_tot) +
  geom_line(data = stab_troph_pred) +
  geom_ribbon(data = stab_troph_pred,
    aes(ymin = conf.low, ymax = conf.high, color = NULL, group = troph_group),
    alpha = .2) +
  annotate("text", x = 0.8, y = .8, label = make_label_rsq(rsq = stab_troph_sum),
    parse = TRUE) +
  #scale_x_log10() + scale_y_log10() +
  labs(x = richness_lab, y = stab_lab)

@@

```{r p-p-div}
lim_log_bm <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_bm_std")

p_bm_div <- sem_data %>%
  ggplot(aes(x = log_rich_tot_std, y = log_bm_std))+
  geom_point() +
  ylim(lim_log_bm) +
  xlim(lim_log_rich_tot) +
  labs(x = richness_lab, y = bm_lab) +
  geom_line(data = bm_div_pred) +
  geom_ribbon(data = bm_div_pred, aes(ymin = conf.low, ymax = conf.high), fill
  = "grey20", alpha = .2) +
  annotate("text", x = .8, y = 1.5, label = make_label_rsq(rsq = bm_div_sum),
    parse = TRUE)

p_bm_div_troph <- stab_div_troph %>%
  ggplot(aes(x = log_rich_tot_std, y = log_bm_std, color = troph_group)) +
  geom_point() +
  ylim(lim_log_bm) +
  xlim(lim_log_rich_tot) +
  ggplot2::scale_color_manual(
    labels = troph_group_labeller(),
    values = c("blue", "green", "red"),
    name = "Trophic group"
  ) +
  geom_line(data = bm_troph_pred) +
  geom_ribbon(data = bm_troph_pred,
    aes(ymin = conf.low, ymax = conf.high, color = NULL, group = troph_group),
    alpha = .2) +
  annotate("text", x = 0.8, y = 1.5, label = make_label_rsq(rsq = bm_troph_sum),
    parse = TRUE) +
  #scale_x_log10() + scale_y_log10() +
  labs(x = richness_lab, y = bm_lab)
